%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Kranthi Kumar Dande} \\ \vspace{10pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-8978706271~
    \href{mailto:kranthikeyadande@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{kranthikeyadande@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/kranthi-kumar-dande-615502279/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn/Kranthi Kumar Dande}} ~
    \href{https://github.com/kranthikeya}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub/kranthikeya}}
\end{center}

%-----------CAREER OBJECTIVE-----------
\section{Career Objective}
\resumeSubHeadingListStart
    \resumeItem{Enthusiastic software developer skilled in the MERN stack, with a talent for problem-solving and creating user-focused applications. Eager to apply my expertise to build high-quality, innovative solutions that enhance user experience and drive results.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Chaitanya Bharathi Institute of Technology}{Nov. 2022 -- Jun. 2025}
      {Bachelor of Engineering in Information Technology}{GPA: 8.0/10.0}
    \resumeSubheading
      {VMR Polytechnic College}{2019 -- 2022}
      {Diploma in Computer Science Engineering}{Percentage: 9.4/10.0}
    \resumeSubheading
      {Jawahar Navodaya Vidyalaya - Siddipet}{2018 -- 2019}
      {Central Board of Secondary Education (CBSE)}{Percentage: 85.0}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Food-Del}}{July 2024}
    \resumeItemListStart
        \resumeItem{Developed a fully responsive website using the MERN stack for a seamless user experience across devices.}
        \resumeItem{Implemented a user-friendly interface with advanced search filters for easy navigation and selection of food items.}
    \resumeItemListEnd

    \resumeProjectHeading{\textbf{AgVenture}}{October 2022 -- April 2023}
    \resumeItemListStart
        \resumeItem{Developed AgVenture, an online platform for crop product trading, facilitating transactions between farmers and customers.}
        \resumeItem{Built using technologies: Django.}
    \resumeItemListEnd

    \resumeProjectHeading{\textbf{Laptop Price Prediction}}{}
    \resumeItemListStart
        \resumeItem{Built an optimal platform to check the daily prices of laptops on various online websites.}
        \resumeItem{Tools \& technologies used: ML stack (Python, MongoDB, HTML, CSS).}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages:} Python, Java \\
        \textbf{Development and Frameworks:} Bootstrap, HTML, CSS, JavaScript, React, Express.js, Node.js \\
        \textbf{Databases:} MongoDB, MySQL \\
        \textbf{Systems:} Experience with Linux and Windows \\
        \textbf{Productive Skills:} Data Structures and Algorithms, Object-Oriented Programming, Machine Learning, Database Management System, SQL \\
        \textbf{Cloud Technologies:} AWS Cloud
    }}
\end{itemize}

%-----------COURSES AND CERTIFICATIONS-----------
\section{Courses \& Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
\begin{minipage}[t]{0.48\textwidth}
    \small{\item{
        \textbf{Courses:} \\
        Data Structures and Algorithms \\
        MERN Stack \\
        Python \\
        Machine Learning \\
        \textbf{LeetCode:} Solved around \textbf{200+} problems
    }}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \small{\item{
        \textbf{Certifications:} \\
        Codegnan Internship: Machine Learning (Intern) \\
        Infosys Springboard: Artificial Intelligence Foundation Certification \\
        Infosys Springboard: Machine Learning Foundation Certification \\
        EDSPREAD: MERN Stack Development Certification
    }}
\end{minipage}
\end{itemize}

%-----------FREELANCER EXPERIENCE-----------
\section{Freelancer Experience}
 \begin{itemize}[leftmargin=0.15in, label={}]
     \resumeProjectHeading
          {\textbf{Valam, August 2024 – Septemper 2024 (frontend-developer) }}{}
          \resumeItemListStart
            \resumeItem{developed Forntend for online platform for Cab serives, Built a responsive user interface using react.js  }

%-----------EXTRA-CURRICULAR-----------
\section{Extra-Curricular}
\resumeSubHeadingListStart
    \resumeItemListStart
        \resumeItem{Mentored undergraduates in Data Structures and Algorithm development, aiding them in improving coding proficiency and problem-solving skills.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
